\documentclass{article}

\usepackage{amssymb,amsmath,longtable, gensymb}

\usepackage{enumitem}
\setlist{parsep=0pt,listparindent=\parindent}

\usepackage[pdftex]{graphicx}
\graphicspath{ {Images/} {Images/eLoss/} {Images/CoordSys/} {Images/TrackerPics/} {Images/Field/} {Images/TrackingFlow/} {Images/LeftRight/} {Images/Misc/}}

\usepackage[margin=1in]{geometry}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=red,
    urlcolor=blue,
    citecolor=blue
}

\usepackage[backend=biber,sorting=none]{biblatex}
\addbibresource{mybib.bib}



\begin{document}

\title{Geane Track Fitting}
\author{Nicholas Kinnaird \\ nickkinn@bu.edu}
\date{\today}
\maketitle

% \renewcommand{\abstractname}{Different Abstract Name}
\begin{abstract}

    In this document I will detail the concepts and mathematics of GEANE track fitting, as well as it's implementation in the gm2 simulation framework for the Muon g-2 Experiment at Fermilab. I will also detail the pecularities and intricacies of the code. This is done both for documentation purposes as well as a precursor to sections of my future thesis. This document assumes some familiarity with art on part of the reader, though such knowledge is not necessary for many sections. Note that the tracking code and framework is in constant development, so the details contained here within may be outdated at time of reading. I've tried to be thorough in my descriptions, but it is possible that some finer points have been left out of this document.

\end{abstract}


\input{Intro.tex}

\input{Formalism.tex}

\input{Framework.tex}

\input{gm2Geane.tex}

\input{LeftRight.tex}

\input{CoordSys.tex}

% \input{NotesOther.tex}

\input{ToDo.tex}

\printbibliography

\section{Acknowledgements}

	I'd like to a thank a number of people who helped me in this track fitting work, without whom this would not have been possible. Since this is not my thesis and more of a technical document, I will keep it brief though these people deserve more words. Thanks to Lee Roberts for the opportunity to work in physics on Muon g-2 and the constant support. Thanks to Rob Carey for the introduction to this project, and the constant advice and input. Thanks to Rob Kutschke for being a source of tracking expertise. Thanks to Joe Price for help with the code. Finally, thanks to James Mott for the endless patience, advice, direction, day-to-day help, and support, without which I believe I would have given up long ago.

\input{Appendix.tex}

\input{Plots.tex}


\end{document}
